Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2014-12-31 evaluation.tex
Update data.

% Flex UMC sweep
\begin{figure}
  \begin{center}
    \vspace{-0.1in}
    \includegraphics[width=\linewidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_fpga_umc_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage versus varying overhead budget for UMC running on an FPGA-based monitor.}
    \label{fig:evaluation.fpga_umc_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \vspace{-0.1in}
  \subfloat[Overhead budget error.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_umc_exec_time.pdf}
    \label{fig:evaluation.umc_exec_time}
  }
  \\
  \subfloat[Coverage.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_umc_coverage.pdf}
    \label{fig:evaluation.umc_coverage}
  }
  \caption{Comparing dropping policies for UMC.}
  \vspace{-0.2in}
  \end{center}
  \label{fig:evaluation.umc_policies}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \vspace{-0.1in}
  \subfloat[Overhead budget error.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_bc_exec_time.pdf}
    \label{fig:evaluation.bc_exec_time}
  }
  \\
  \subfloat[Coverage.]{
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_bc_coverage.pdf}
    \label{fig:evaluation.bc_coverage}
  }
  \caption{Comparing dropping policies for BC.}
  \vspace{-0.2in}
  \end{center}
  \label{fig:evaluation.bc_policies}
\end{figure}

@@

>>>>

% Flex UMC sweep
\begin{figure}
  \begin{center}
    \vspace{-0.1in}
    \includegraphics[width=\linewidth]{figs/data_fpga_umc_sweep.pdf}
    \vspace{-0.2in}
    \caption{Coverage versus varying overhead budget for UMC running on an FPGA-based monitor.}
    \label{fig:evaluation.fpga_umc_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \vspace{-0.1in}
  \subfloat[Overhead budget error.]{
    \includegraphics[width=\columnwidth]{figs/data_umc_overhead.pdf}
    \label{fig:evaluation.umc_exec_time}
  }
  \\
  \subfloat[Coverage.]{
    \includegraphics[width=\columnwidth]{figs/data_umc_coverage.pdf}
    \label{fig:evaluation.umc_coverage}
  }
  \caption{Comparing dropping policies for UMC.}
  \vspace{-0.2in}
  \end{center}
  \label{fig:evaluation.umc_policies}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \vspace{-0.1in}
  \subfloat[Overhead budget error.]{
    \includegraphics[width=\columnwidth]{figs/data_hb_overhead.pdf}
    \label{fig:evaluation.bc_exec_time}
  }
  \\
  \subfloat[Coverage.]{
    \includegraphics[width=\columnwidth]{figs/data_hb_coverage.pdf}
    \label{fig:evaluation.bc_coverage}
  }
  \caption{Comparing dropping policies for BC.}
  \vspace{-0.2in}
  \end{center}
  \label{fig:evaluation.bc_policies}
\end{figure}

@@

% Runtime power of monitoring core
\begin{table}[tb]
  \begin{center}
    \vspace{-0.0in}
    \begin{footnotesize}
    \input{tabs/monitor_power}
    \end{footnotesize}
    \caption{Average runtime power of the monitoring core.}
    \vspace{-0.2in}
    \label{tab:evaluation.monitor_power}
  \end{center}
\end{table}

Table~\ref{tab:evaluation.monitor_power} shows the runtime power usage of the
monitoring core averaged across all benchmarks. These results are shown for an
overhead target of 1.5x as well as when full monitoring is performed.
